---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# datavyu

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/datavyu)](https://CRAN.R-project.org/package=datavyu)
[![Travis build status](https://travis-ci.com/tca2/datavyu.svg?branch=master)](https://travis-ci.com/tca2/datavyu)
<!-- badges: end -->

The goal of {datavyu} is to to  to facilitate the use of the open-source **datavyu** software for the analysis of qualitative audiovisual data. This package extensively uses [{datavyur}](https://github.com/iamamutt/datavyu) for preparing the data for the summary statistic and plotting functions in this package. We do not intend to duplicate the functionality of that excellent package in ours; we focus instead on summarizing datavyu output and preparing the output for use in other analyses.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tca2/datavyu")
```

The datavyu software must also be installed; see [here](https://datavyu.org/download.html)

## Preparing files for analysis within datavyu

```{r}
library(dplyr)
library(datavyur)
```

```{r, echo = FALSE}
devtools::load_all(".")
```

*note*: The use of this package requires the use of the **datavyu** software's [Ruby API](https://datavyu.org/user-guide/api.html); note that while **datavyu** has a graphical user interface, it is accompanied by a number of Ruby scripts.

#### 1. Run the following Ruby script within the datavyu software by selecting Script and then Run Script; select a directory with one or more `.opf` files:

`csv2opf.rb`

<!-- I ran this on the Empirical Analyses folder to generate a bunch of data -->

#### 2. Open the directory that the Ruby script created; a number of CSV files for each `.opf` file should now be created.

This is the directory (folder) passed to the datavyu functions below.

## Exploring the columns and files

Using {datavyu}, you can find the unique columns across all of the files in a directory:

```{r}
find_unique_columns("ex-data/datavyu_output_07-06-2020_14-46")
```

You can also find unique files

```{r}
find_unique_files("ex-data/datavyu_output_07-06-2020_14-46")
```

## Summarizing a column

{datavyu} can help to summarize a column. It defaults to summarizing 
the frequency of codes for a specified column.

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 directory = "ex-data/datavyu_output_07-06-2020_14-46")
```

Because `summary_column()` returns a tibble/data.frame, it can be computed on:

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 directory = "ex-data/datavyu_output_07-06-2020_14-46") %>% 
  filter(!str_detect(log_class_as_activity_format_code01, "[?]")) # note that names are cleaned upon being processed
```

We can also explore the frequencies *by file* by changing the `by_file` argument to 
`TRUE`.

We'll be typing that folder file path a number of times; you can set an option 
that will mean that the folder file path you set will be used *by default*, though
you can over-ride it any time you like.

```{r}
options(directory = "ex-data/datavyu_output_07-06-2020_14-46")
```

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 by_file = TRUE)
```

To summarize durations (instead of frequencies) by changing the `summary` argument,
which defaults to `"frequency"`, but can be changed to `"duration"`:

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 summary = "duration")
```

```{r}
x <- summarize_column(column = "LogClass_AS_ActivityFormat",
                      summary = "duration")
```

Columns can also be summarized by file:

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 by_file = TRUE,
                 summary = "duration")
```

## Ploting the results of a summary of a column

{datavyu} can also help to plot the summary of a column. Here, we save the output
from `summarize_column()` to an object (we call this `freq_summary`, but it can 
be named whatever we like). 

Then, we use this output in the function `plot_column_summary()`:

```{r, eval}
freq_summary <- summarize_column(column = "LogClass_AS_ActivityFormat")

plot_column_summary(freq_summary)
```

This also works by file---so long as the column is summarized by file:

```{r}
freq_summary <- summarize_column(column = "LogClass_AS_ActivityFormat",
                                 by_file = TRUE, summary = "duration")

freq_summary <- filter(freq_summary,
                       !str_detect(log_class_as_activity_format_code01, "[?]"))

plot_column_summary(freq_summary)
```

It is also possible to summarize across all of the data, or another variable (in-development):

```{r, eval = FALSE}
plot_column_summary(duration_summary, summarize_across = "all")
```

Will plot the means and standard errors of the means for each level of each code.

Similarly, if the output is for the duration, rather than the frequency, the durations are plotted:

```{r}
duration_summary <- summarize_column(column = "LogClass_AS_ActivityFormat",
                                     summary = "duration")

plot_column_summary(duration_summary)
```

Like for frequency, these can be ploted by file:

```{r}
duration_summary_by_file <- summarize_column(column = "LogClass_AS_ActivityFormat",
                                             summary = "duration",
                                             by_file = TRUE)

plot_column_summary(duration_summary_by_file)
```

## Using the pipe operator

Finally, output can be passed between functions with the pipe operator:

```{r}
summarize_column(column = "LogClass_AS_ActivityFormat",
                 summary = "duration",
                 by_file = TRUE) %>% 
  plot_column_summary()
```

## Time series preparation and plot (in-development)

```{r, eval = FALSE}
prep_time_series() %>%
  plot_time_series()
```

## Features in-development

- Plotting code co-occurrences with `plot_cooccurence()`
- Summarizing an entire file (not just a single column in a file) with `summarize_file()`
- Addressing a number of [issues](https://github.com/tca2/datavyu/issues), including some that relate to the {datavyur} package

## Contributing

Please note that the datavyu project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## pkgdown website

Because this repository is private, the [{pkgdown}](https://pkgdown.r-lib.org/)-generated website for this package
is available only in the `/docs` directory. Drag the `index.html` file in that directory into a browser to view this site.

## Acknowledgment

This material is based upon work supported by the National Science Foundation under [Grant No. 1920796](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1920796&HistoricalAwards=false). Any opinions, findings, conclusions, or recommendations expressed in this material are those of the authors and do not reflect the views of the National Science Foundation.
