---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)

devtools::load_all(".")
```

# datavyu

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/datavyu)](https://CRAN.R-project.org/package=datavyu)
[![Travis build status](https://travis-ci.com/tca2/datavyu.svg?branch=master)](https://travis-ci.com/tca2/datavyu)
<!-- badges: end -->

The goal of {datavyu} is to to  to facilitate the use of the open-source **datavyu** software for the analysis of qualitative audiovisual data. This package extensively uses [{datavyur}](https://github.com/iamamutt/datavyu) for preparing the data for summary statistics and plotting functions in this package. We do not intend to duplicate the functionality of that excellent package; instead we focus on summarizing datavyu output and preparing the output for use in other analyses.

## Installation

First, install the datavyu software; see [here](https://datavyu.org/download.html)

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tca2/datavyu")
```

```{r, eval = FALSE}
library(datavyu)
```

## Preparing data for analysis

Please see the [preparing data](preparing-data.html) vignette to use the datavyu software to prepare the native `.opf` files for analysis here.

## Exploring the columns and files

Using {datavyur} (not this package, but one that this package - {datavyu} - relies on), you can find information on all of the files (and their columns and codes) in a given directory:

```{r}
library(datavyur)

summary_of_files <- datavyur::datavyu_col_search("ex-data/datavyu_output_11-16-2020_13-26")

summary_of_files
```

We can easily find _distinct_ files and columns using {dplyr} function `distinct()`:

```{r}
library(dplyr)

summary_of_files %>% 
  distinct(file)

summary_of_files %>% 
  distinct(column)
```


## Summarizing a column

{datavyu} can help to summarize a column. It defaults to summarizing 
the frequency of codes for a specified column.

Note that, by default, the code name combines the column and code names; so, the `hand` code in the above summary would be combined with its column `childhands` (or `parenthands`) to be specified as `childhands_hand` or `parenthands_hand`:

```{r}
summarize_column(column = "childhands",
                 code = "childhands_hand",
                 directory = "ex-data/datavyu_output_11-16-2020_13-26")
```

---

We can also explore the frequencies *by file* by changing the `by_file` argument to 
`TRUE`.

We'll be typing that folder file path a number of times.  You can set an option 
that let the folder file path you set be used *by default*, though
you can over-ride it any time you like.

```{r}
options(directory = "ex-data/datavyu_output_11-16-2020_13-26")
```

Then, use this default by changing the the `by_file` argument to `TRUE`: 

```{r}
summarize_column(column = "childhands",
                 code = "childhands_hand",
                 by_file = TRUE)
```

---

To summarize durations (instead of frequencies) change the `summary` argument(defaults as `"frequency"`) to `"duration"`:

```{r}
summarize_column(column = "childhands",
                 code = "childhands_hand",
                 summary = "duration")
```

Columns of durations can also be summarized by file:

```{r}
summarize_column(column = "childhands",
                 code = "childhands_hand",
                 by_file = TRUE,
                 summary = "duration")
```

## Ploting the results of a summary of a column

{datavyu} can also help to plot the summary of a column. Here, we save the output
from `summarize_column()` to an object (we call this `freq_summary`, but it can 
be named whatever we like). 

Then, we use this output in the function `plot_column_summary()`:

```{r, eval}
freq_summary <- summarize_column(column = "childhands", code = "childhands_hand")

plot_column_summary(freq_summary)
```

This also works by file---so long as the column is summarized by file:

```{r}
freq_summary <- summarize_column(column = "childhands", code = "childhands_hand",
                                 by_file = TRUE, summary = "duration")

plot_column_summary(freq_summary)
```

Similarly, if the output is for the duration, rather than the frequency, the durations are plotted:

```{r}
duration_summary <- summarize_column(column = "childhands", code = "childhands_hand",
                                     summary = "duration")

plot_column_summary(duration_summary)
```

Like for frequency, these can be ploted by file:

```{r}
duration_summary_by_file <- summarize_column(column = "childhands", 
                                             code = "childhands_hand",
                                             summary = "duration",
                                             by_file = TRUE)

plot_column_summary(duration_summary_by_file)
```

## Using the pipe operator

Finally, output can be passed between functions with the pipe operator:

```{r}
summarize_column(column = "childhands", 
                 code = "childhands_hand",
                 summary = "duration",
                 by_file = TRUE) %>% 
  plot_column_summary()
```

## Time series preparation and plot (in-development)

To visualize frequency of a certain coded datavyu column accounting for the duration of the video, we can use the function `plot_time_series()`. First we must prepare the data via saving the `prep_time_series()` function as an object (here we use `prepared_time_series`).

Note that the available files can be found using `datavyur::datavyu_col_search()` (described above):

```{r}
prepared_time_series <- prep_time_series(column = "childhands",
                                         code = "childhands_hand",
                                         specified_file = "dyad1")

prepared_time_series
```

The `units` argument defaults to "s" (seconds), but can be changed to "m" (rounds the data to minutes) 
or "ms" (retains datavyu's default units, milliseconds).

We can see how using milliseconds increases the number of data points:

```{r}
prepared_time_series_ms <- prep_time_series(column = "childhands",
                                            code = "childhands_hand",
                                            specified_file = "dyad1",
                                            units = "ms")

prepared_time_series_ms
```
Your `prepared_time_series_ms` object can now be plotted usinf the `plot_time_series()` function.  Here is an example of how time series data can be represented, utilizing the functions defaulted unit value of seconds:

```{r}
plot_time_series(prepared_time_series)
```

## Features in-development

- interrater
- by file `prep_time_series()`
- Plotting code co-occurrences with `plot_cooccurence()`
- Summarizing an entire file (not just a single column in a file) with `summarize_file()`
- Addressing a number of [issues](https://github.com/tca2/datavyu/issues), including some that relate to the {datavyur} package

## Contributing

Please note that the datavyu project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## pkgdown website

Because this repository is private, the [{pkgdown}](https://pkgdown.r-lib.org/)-generated website for this package
is available only in the `/docs` directory. Drag the `index.html` file in that directory into a browser to view this site.

## Acknowledgment

This material is based upon work supported by the National Science Foundation under [Grant No. 1920796](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1920796&HistoricalAwards=false). Any opinions, findings, conclusions, or recommendations expressed in this material are those of the authors and do not reflect the views of the National Science Foundation.
