---
title: "Calculating Interrater Agreement"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating Interrater Agreement}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 250
)
```

# Loading, setting up

First, load the {datavyu} and {datavyur} packages and the {tidyverse} suite of packages:

```{r setup, message=F}
library(datavyu)
library(datavyur) # (install via `devtools::install_github("iamamutt/datavyu/datavyur")`)
library(tidyverse) # install via install.packages("tidyverse")
library(irr) # install via install.packages("irr")
library(patchwork) # install via install.packages("patchwork")
library(here) # install.packages("here")
```

## Preparing the data in datavyu (the software---not the package!)

Next, let's prepare the files we wish to analyze. To do so, we have to export them from the datavyu software, as follows:

1. Run the following Ruby script within the datavyu software by selecting Script and then Run Script; select a directory with one or more `.opf` files:

`csv2opf.rb`

## 2. Open the directory that the Ruby script created; a number of CSV files for each `.opf` file should now be created.

This is the directory (folder) passed to the datavyu functions below.

The [{here} package](https://here.r-lib.org/) can be used to flexibly (across computers/operating systems) specify file paths: To save on typing, the directory can be set for an entire R session via the following:

```{r}
options(directory = here("irr-data", "datavyu_output_11-16-2020_14-13"))
```

# Summarizing a column

Frequency of codes; note that the code is the code listed appended to the column name after a period.

Note that you may wish to look at the names of the files, columns, and codes; the following function can be used to do that:

```{r, eval = FALSE}
datavyu_col_search(here("irr-data", "datavyu_output_11-16-2020_14-13"))
```


```{r}
summarize_column(column = "LogClass_IS",
                 code = "LogClass_IS.i")
```

Frequency of codes by file:

```{r}
summarize_column(column = "LogClass_IS",
                 code = "LogClass_IS.i",
                 by_file = TRUE)
```

Plot of duration (note that `summary = "duration"` can be added to any of the above) by file:

```{r}
freq_summary <- summarize_column(column = "LogClass_IS",
                                 code = "LogClass_IS.i",
                                 by_file = TRUE,
                                 summary = "duration")

plot_column_summary(freq_summary)
```

# Inter-rater agreement

## Plots

```{r}
prepared_time_series_tm <- prep_time_series(column = "LogClass_IS",
                                            code = "LogClass_IS.i",
                                            specified_file = "TM 14-12-03 T201 Content Log")

plot_time_series(prepared_time_series_tm)

prepared_time_series_hh <- prep_time_series(column = "LogClass_IS",
                                            code = "LogClass_IS.i",
                                            specified_file = "HH T201 14-12-03 Content Log")

plot_time_series(prepared_time_series_hh)

```
These could be composed together using the patchwork library:

```{r}
plot_time_series(prepared_time_series_tm) +
  plot_time_series(prepared_time_series_hh) +
  plot_layout(ncol = 1)
```

## Agreement statistics

First, looking at data:

```{r}
prepared_time_series_tm
prepared_time_series_hh
```

We'll do a ["full" join](https://dplyr.tidyverse.org/reference/join.html), re] taining all time stamps for both files. First, we must rename one (or both) of the two `code` columns. Having done this, we can easily compare the two once joined:

```{r}
prepared_time_series_tm <- rename(prepared_time_series_tm, code_tm = code)
prepared_time_series_hh <- rename(prepared_time_series_hh, code_hh = code)

joined_data <- prepared_time_series_tm %>% 
  full_join(prepared_time_series_hh, by = "ts")

joined_data
```

We can calculate agreement using the {irr} package, passing only the 2nd and 3rd columns (with the codes) to the function `agree()` (from the {irr} function):

```{r}
agree(joined_data[, 2:3])
```

We can do the same for Cohen's Kappa using the `kappa2` statistic:

```{r}
kappa2(joined_data[, 2:3])
```
