---
title: "Time Series Plots"
author: "Alex Lishinski"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
vignette: |
  %\VignetteIndexEntry{Time Series Plots} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basics of Time Series Plots

The `plot_time_series` function allows for plotting of time series data in the form of time series data .csv files accessed via `datavyur::import_datavyu`.

The default plot using 1 column puts each code on a separate line:

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(birdseyevyu)
library(here)

plot_time_series(directory =  here("inst", "extdata", "2021-03-28-ex", "datavyu_output"), columns = "LogClass_AS_ActivityFormat", colors = "Set3")
```

When using more than 1 column, each column is on a separate line:

```{r,warning=FALSE, message=FALSE}
plot_time_series(directory =  here("inst", "extdata", "2021-03-28-ex", "datavyu_output"), columns = c("LogClass_AS_ActivityFormat", "LogClass_AS_ParticipationFormat"), colors = "Set3")
```

### Basic Color Palettes

You can select one of the preexisting palettes that are part of `scale_color_brewer()`, using the `colors` argument and the number or name of these palettes. 

```{r}
plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = "LogClass_IG")
plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = "LogClass_IG", colors = 2)
plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = "LogClass_IG", colors = 3)
``` 

This only works if there are 8 or less codes to be plotted. If there are 9 or more codes, the function defaults back to `scale_color_discrete()`, which picks evenly spaced colors from the color wheel.

```{r}
plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = c("LogClass_IG", "LogClass_AS_ParticipationFormat"), colors = 2)
```

### Custom Code Colors

You can now put the codes in a different order by specifying a character vector with the order you want using the `cat_order` argument. 

```{r}
order <- c("n" , "b" , "y", "o" , "g" , "r")

plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = "LogClass_IG", cat_order = order)
```

You can also pick colors completely manually by providing the hex codes for whatever colors you want using the `color_scale` argument. Doing this will also order the codes from top to bottom using the order provided, as with the `cat_order` argument.

```{r}
colors <- c("n" = "#FFF430", "b" = "#9C59D1", "y" = "#000000", "o" = "#D00070", 
            "g" = "#8C4799", "r" = "#0032A0")

plot_time_series(directory = here("inst", "extdata", "data", "datavyu_output"), columns = "LogClass_IG", color_scale = colors)
```

